Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
updated caption of baroclinicity plot
more results

Table~\ref{table:sim_names} summarizes the simulations that we ran.
The majority of them used a reaction rate boosting of $10$ and a
conductivity boosting of $10$, which should increase the flame speed
by a factor of $10$.  Most simulations used a resolution of
$10~\mbox{cm}$ and a domain width of a little more than one kilometer.  
We use an artifically high rotation rate of
$2000~\mbox{Hz}$, which gives a Rossby length of
\begin{equation}
L_R = \frac{\sqrt{g H_0}}{\Omega} \sim 3\times 10^4~\mathrm{cm}
\end{equation}
using a scale height $H_0 = 10^3~\mathrm{cm}$.  This is about one
quarter of domain width.  The run at $20~\mbox{cm}$ resolution used
one fewer level of refinement.  The slower rotating case using a
slightly wider domain to accommodate the expected larger Rossby
length.  We note that the entire simulation framework for these
calculations is freely available in the \castro\ github
repository\footnote{\url{https://github.com/AMReX-Astro/Castro}}.

@@

\AssignTo{Mike, Kiran, Alice}

Figure~\ref{fig:time_series} shows the time \MarginPar{this plot needs a description}

Here we'll show the large scale dynamics, colormap plots, etc. and discuss the trends.

@@

% made with overview.py
\begin{figure}[h]
\centering
\plotone{flame_wave_boost_10_10_overview}
\caption{\label{fig:10_10_overview} Temperature, energy generation rate, and out-of-plane velocity for the 10/10 simulation.}
\end{figure}

% made with slice_multi_crop.py
\begin{figure}[h]
\centering
\plotone{flame_wave_boost_10_10_lowres_slice}
\caption{\label{fig:10_10_lowres} Temperature, mean molecular weight, energy generation rate, and out-of-plane velocity for the 10/10 low resolution simulation.}
\end{figure}

@@

\subsection{Resolution}

\MarginPar{talk about the low res run?}

Our default resolution puts $\sim 50$ zones vertically in the ``cool''
model atmosphere height.  To understand the effects of resolution, we
also perform a run with one additional level, with a $2\times$ jump
refining just the region where the density is $10^4~\gcc < \rho \le
4\times 10^4~\gcc$.  On this level, the grid resolution is
$10~\mathrm{cm}$.

>>>>

Table~\ref{table:sim_names} summarizes the simulations that we ran.
The majority of them used a reaction rate boosting of $10$ and a
conductivity boosting of $10$, which should increase the flame speed
by a factor of $10$.  Most simulations used a resolution of
$10~\mbox{cm}$ and a domain width of a little more than one kilometer.  
We use an artifically high rotation rate of
$2000~\mbox{Hz}$, which gives a Rossby length of
\begin{equation}
L_R = \frac{\sqrt{g H_0}}{\Omega} \sim 3\times 10^4~\mathrm{cm}
\end{equation}
using a scale height $H_0 = 10^3~\mathrm{cm}$.  This is about one
quarter of domain width.  The run at $20~\mbox{cm}$ resolution used
one fewer level of refinement.  The slower rotating case using a
slightly wider domain to accommodate the expected larger Rossby
length.  We note that the entire simulation framework for these
calculations is freely available in the \castro\ github
repository\footnote{\url{https://github.com/AMReX-Astro/Castro}, using
  the {\tt flame\_wave} setup.}.  In the discussions below, we'll use
the simulation names defined in the table to refer to specific runs
and we'll use the 10/10 run as the reference calculation.

@@

Figure~\ref{fig:time_series} shows the time evolution of the 10/10
simulation, focusing on the mean-molecular weight,
\begin{equation}
\bar{A} = \left ( \sum_k \frac{X_k}{A_k} \right )^{-1}
\end{equation}
In each frame the buffer of \isot{Ni}{56} that serves as the
underlying neutron star is seen spanning the bottom of the domain.
Above that, the composition begins as pure \isot{He}{4}, but as the
simulation progresses, the flame processes this to heavier nuclei,
increasing $\bar{A}$.  By about $10~\mbox{ms}$, we see the flame front
is reasonable well-defined.  We see that the bottom of the burning
front is listed off of the base of the atmosphere, greatly increasing
the surface area of the burning compared with a perfectly vertical
flame front.  By $20~\mbox{ms}$ the flame has moved out substantially
and we are beginning to see a gradient in the composition of the ash,
with the heavier nuclei furthest behind the flame.  The boosting of
the burning likely artificially increases this effect.

@@

Figure~\ref{fig:10_10_overview} shows the temperature, energy
generation rate, and $w$ component of the velocity (the out-of-plane
velocity induced by the Coriolis force).  This latter field
illustrates the hurricane effect setup by the laterally spreading
burning front.  In the energy generation rate plot, we see that the
burning is mostly concentrated toward the bottom of the layer, as
expected since the density is greatest there.  We see that the peak of
the burning has moved off of the symmetry axis, demonstrating that the
burning front is propagating to the right.  In the temperature plot,
we see the effect of our refinement criteria focusing only on the
atmosphere where we are most dense, with an artificial drop in the
temperature at the refinement boundary likely due to the thermal
diffusion.  As we'll see when the lower resolution case, we do not
believe that this affects the results.

% made with overview.py
\begin{figure}[h]
\centering
\plotone{flame_wave_boost_10_10_overview}
\caption{\label{fig:10_10_overview} Temperature, energy generation rate, and out-of-plane velocity for the 10/10 simulation at 20~ms.}
\end{figure}

Our default resolution puts $\sim 100$ zones vertically in the
``cool'' \MarginPar{double check} model atmosphere height.  To
understand the effects of resolution, we also perform a run with one
fewer level, giving at $20~\mbox{cm}$ resolution overall.  Figure~\ref{fig:10_10_lowres}
shows the fields at 20~ms.

% made with slice_multi_crop.py
\begin{figure}[h]
\centering
\plotone{flame_wave_boost_10_10_lowres_slice}
\caption{\label{fig:10_10_lowres} Temperature, mean molecular weight,
  energy generation rate, and out-of-plane velocity for the 10/10 low
  resolution simulation at 20~ms.}
\end{figure}

@@
